Rigidity of Expectation Formation: Additional Evidence from Desntify Forecasts

### 2019-06-27 paper/Draft.tex
finalizing charts on dispersion.
Finalizing on histograms of revisions of SPF.

We drop the outliers of uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=8cm]{figures/IQRvarCPIQ.png} \\
	\smallskip
	\includegraphics[width=8cm]{figures/IQRvarPCEQ.png}\\
		\smallskip
	\includegraphics[width=8cm]{figures/IQRvarSCEM.png}\\
	\caption{Dispersion in Mean Forecast and Unceratinty }
	\label{IQR_Unceratitny}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=7cm]{figures/PRCCPIMean_rv_hist.png} 
	\includegraphics[width=7cm]{figures/PRCCPIVar_rv_hist.png}  \\
	\smallskip
	\includegraphics[width=7cm]{figures/PRCPCEMean_rv_hist.png} 
	\includegraphics[width=7cm]{figures/PRCPCEVar_rv_hist.png}  \\
	\caption{Distribution of Revision in Forecasts}
	\label{RevisionHist}
\end{figure}

>>>>

For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.   For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extream values. \footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in totla.}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=7cm]{figures/IQRmeanCPIQ.png} 
	\includegraphics[width=7cm]{figures/IQRvarCPIQ.png} \\
	\smallskip
   \includegraphics[width=7cm]{figures/IQRmeanPCEQ.png}
	\includegraphics[width=7cm]{figures/IQRvarPCEQ.png}\\
		\smallskip
		\includegraphics[width=7cm]{figures/IQRmeanSCEM.png}
	\includegraphics[width=7cm]{figures/IQRvarSCEM.png}\\
	\caption{Dispersion in Mean Forecast and Unceratinty }
	\label{IQR_Unceratitny}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=7cm]{figures/PRCCPIMean01_rv_true_hist.png} 
	\includegraphics[width=7cm]{figures/PRCCPIVar01_rv_true_hist.png}  \\
	\smallskip
	\includegraphics[width=7cm]{figures/PRCPCEMean01_rv_true_hist.png} 
	\includegraphics[width=7cm]{figures/PRCPCEVar01_rv_true_hist.png}  \\
	\caption{Distribution of Revision in Forecasts}
	\label{RevisionHist}
\end{figure}
